### 2013-02-16 doc/icml2013/intro.tex
Changes to Lemma 2

% Norms
For a matrix $X$,
let $\|X\|_*$ denote the nuclear (trace) norm (sum of singular values),
let $\|X\|_F$ denote the Frobenius norm (square root of sum of squares of singular values),
let $\|X\|_\text{op}$ denote the operator norm (largest singular value).
For a rank-$K$ tensor $X$,
let $\|X\|_* = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_*$ denote
the average nuclear norm over all $p$ unfoldings,
and let $\|X\|_\text{op} = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_\text{op}$
denote the average operator norm over all $p$ unfoldings.
Let $\sigma_\text{min}(X)$ be the smallest singular value of $X$.

>>>>

% Norms
For a matrix $X$,
let $\|X\|_*$ denote the nuclear (trace) norm (sum of singular values),
let $\|X\|_F$ denote the Frobenius norm (square root of sum of squares of singular values),
let $\|X\|_{\max}$ denote the max norm (elementwise maximum),
let $\|X\|_\text{op}$ denote the operator norm (largest singular value).
For a rank-$K$ tensor $X$,
let $\|X\|_* = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_*$ denote
the average nuclear norm over all $p$ unfoldings,
and let $\|X\|_\text{op} = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_\text{op}$
denote the average operator norm over all $p$ unfoldings.
Let $\sigma_\text{min}(X)$ be the smallest singular value of $X$.

### 2013-02-16 doc/icml2013/regression.tex
Changes to Lemma 2

\paragraph{Low-rank regression}
%\label{sec:regression}
\vspace{-0.5em}
We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.

@@

\begin{lemma}[lower bound on restricted strong convexity]
\label{lem:lowRankLower}
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$.
With probability at least $1-\delta$,
$$\kappa(\opX) = \Omega\left(\sigmamin(\Sigma_p) - d^p R^{p} \sqrt{\frac{p \log(d) \log (1/\delta)}{n}}\right).$$
\end{lemma}
\begin{proof}
Expanding the definition of the observation operator:
$\frac{1}{2n} \|\opX_p(\Delta)\|_2^2
= \frac{1}{2n} \sum_{(x,y) \in \sD} \innerp{\Delta}{x\tp{p}}^2$.
Unfolding the tensor and letting $\hat\Sigma_p \eqdef \frac{1}{n} \sum_{(x,y) \in \sD} \cvec(x\tp{p})\tp{2}$,
we have 
$\frac{1}{2n} \|\opX_p(\Delta)\|_2^2
\ge \frac{1}{2} \trace(\cvec(\Delta)\tp{2} \hat\Sigma_p)
\ge \frac{1}{2} \|\Delta\|_F^2 \sigmamin(\hat\Sigma_p)$.
It remains to show that $\sigmamin(\hat\Sigma_p)$ and $\sigmamin(\Sigma_p)$ are close.
To do this, we first apply Hoeffding's inequality elementwise.
Since $\|x\| \le R$, we have that for each element $(i,j)$,
$|(\hat\Sigma_p)_{ij} - (\Sigma_p)_{ij}| = O(R^{p}\sqrt{\frac{\log (1/\delta)}{n}})$.
Applying the union bound over the $d^{2p}$ elements of $\hat\Sigma_p - \Sigma_p$,
we have that the max norm is bounded:
$\|\hat\Sigma_p - \Sigma_p\|_\text{\rm max} = O(R^{p} \sqrt{\frac{p \log(d) \log (1/\delta)}{n}})$.
The max norm times $d^p$ upper bounds the Frobenius norm, which upper bounds the operator norm, so we have that
$\|\hat\Sigma_p - \Sigma_p\|_\text{\rm op} = O(d^p R^{p} \sqrt{\frac{p \log(d) \log (1/\delta)}{n}})$.
Using the fact that $\sigmamin(\hat\Sigma_p) = \sigmamin(\Sigma_p) + \|\hat\Sigma_p - \Sigma_p\|_\text{\rm op}$
yields the result.
\end{proof}

@@

With these lemmas in hand, we now give the proof of \refthm{convergence}.
\begin{proof}
By \reflem{lowRank} along with \reflem{lowRankLower} and \reflem{lowRankUpper} (discussed below),
we can control the Frobenius norm of the parameter estimates:
If $n \ge n_1$, then
\begin{align}
  \|\hat M_p - M_p\|_F = O\left( \sigma^3 L^3 R^6 k^{\frac12} \sigmamin(\Sigma_p)^{-1} \sqrt{\frac{\log^3 (1/\delta)}{n}} \right).
  %\|\hat M_p - M_p\|_F = O\left( \frac{\sigma^3 L^3 R^6 \sqrt{k} \log^3 (1/\delta)}{\sqrt{n} (\sigmamin(\Sigma_p) - d^p R^p \sqrt{\frac{p \log(d) \log(1/\delta)}{n}}} \right).
\end{align}
The Frobenius norm upper bounds the operator norm,
so we can directly apply Theorem 5.1 of \cite{AnandkumarGeHsu2012}.
%Let $T^* = M_3^*(W^*, W^*, W^*)$.
%Need to convert error from $\epsilon$
%hit by $(W^\top)^\dagger$
\end{proof}

>>>>

\paragraph{Low-rank Regression}
%\label{sec:regression}
\vspace{-0.5em}
We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.

@@

\begin{lemma}[lower bound on restricted strong convexity]
\label{lem:lowRankLower}
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$.
If $$n = \Omega \left( p ~ d^{2p} \log(d) \frac{R^{2p} \log(1/\delta)}{\sigmamin(\Sigma_p)^2} \right),$$
with probability at least $1-\delta$,
$$\kappa(\opX) \ge \frac{\sigmamin(\Sigma_p)}{2}.$$
\end{lemma}
\begin{proof}
Expanding the definition of the observation operator:
$\frac{1}{2n} \|\opX_p(\Delta)\|_2^2
= \frac{1}{2n} \sum_{(x,y) \in \sD} \innerp{\Delta}{x\tp{p}}^2$.
Unfolding the tensor and letting $\hat\Sigma_p \eqdef \frac{1}{n} \sum_{(x,y) \in \sD} \cvec(x\tp{p})\tp{2}$,
we have 
$\frac{1}{2n} \|\opX_p(\Delta)\|_2^2
\ge \frac{1}{2} \trace(\cvec(\Delta)\tp{2} \hat\Sigma_p)
\ge \frac{1}{2} \|\Delta\|_F^2 \sigmamin(\hat\Sigma_p)$.
It remains to show that $\sigmamin(\hat\Sigma_p)$ and $\sigmamin(\Sigma_p)$ are close.
To do this, we first apply Hoeffding's inequality elementwise.
Since $\|x\|_2 \le R$, we have that for each element $(i,j)$,
$|(\hat\Sigma_p)_{ij} - (\Sigma_p)_{ij}| = O(R^{2p}\sqrt{\frac{\log (1/\delta)}{n}})$.
Applying the union bound over the $d^{2p}$ elements of $\hat\Sigma_p - \Sigma_p$,
we have that the max norm is bounded:
$\|\hat\Sigma_p - \Sigma_p\|_\text{\rm max} = O(R^{2p} \sqrt{\frac{p \log(d) \log (1/\delta)}{n}})$.
The max norm times $d^p$ upper bounds the Frobenius norm, which upper bounds the operator norm, so we have that
$\|\hat\Sigma_p - \Sigma_p\|_\text{\rm op} = O(d^p R^{2p} \sqrt{\frac{p \log(d) \log (1/\delta)}{n}})$.
Using the fact that $\sigmamin(\hat\Sigma_p) \ge \sigmamin(\Sigma_p) - \|\hat\Sigma_p - \Sigma_p\|_\text{\rm op}$
yields the result.
\end{proof}

@@
